Manuscript Heat Map Script

### 2025-09-10 ABP_heatmap_for_Cece_20241018.Rmd
Added turbidity heatmap

>>>>

```{r turbidity set up}
CTD_turb <- EDI_CTD %>% 
  select(Reservoir, Site, DateTime, Depth_m, Turbidity_NTU, Date, Year) %>% 
  na.omit() %>% 
  filter(Turbidity_NTU <= 100)

CTD_turb_casts <- CTD_turb |>
  select(Reservoir, DateTime, Year)|>
  mutate(Date = date(DateTime)) %>% 
  distinct(Reservoir, Date, .keep_all = TRUE)

# GEt the month and date for easier graphing. This is not the correct date.   
  CTD_turb_casts$MDay <- format(CTD_turb_casts$DateTime,"%m-%d")
  CTD_turb_casts$MDay <- as.Date(CTD_turb_casts$MDay, "%m-%d")
```

```{r turbidity heat map}

make_turb_heat_map <- function(
    data,
    sample_dates1,
    turnovers,
    y_lim,
    custom_heatmap_palette,
    y_units,
    output_file){

# change the plots dimensions  
jpeg(paste0(output_file),width = 8, height = 4, units = "in", res = 400)
water_temp <- data%>%
  mutate(x = as.Date(x, origin = "1970-01-01"),
         Year = year(x))%>%
  filter(!is.na(z))%>%
  ggplot()+
  geom_raster(aes(x=MDay, y=y,fill = z))+
  geom_point(data = sample_dates1, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") + #to mark cast dates 
   geom_vline(data= turnovers, aes(xintercept=MDay) , linetype="solid", color="black", linewidth=0.5) +
  labs(y = "Depth (m)") +
  scale_x_date(expand = c(0,0)) +
  scale_y_reverse(expand = c(0,0)) +
  #scale_y_continuous(expand = c(0,0))+
  theme(panel.border = element_rect(fill = NA),
        axis.title.x=element_blank())+
  scale_fill_gradientn(name = y_units,
                       limits = y_lim,
                       colours = custom_heatmap_palette,
                       values=rescale(c(0,20,100)))+
  facet_grid(rows= vars(Reservoir),cols = vars(Year),
             scales = "free_y",
             space = "free"
             )+
  theme(panel.background = element_rect(fill = "white"),
          panel.spacing.x = unit(0.05, "lines"),
        legend.position = 'bottom',
        panel.grid = element_blank())
  theme_bw(base_size = 18)
  # labs(color = "")+
  # geom_point(data = sensor_depth_plot, 
  #            aes(x = Date, y = Sensor_depth), 
  #            shape = 23, fill = "black", color = "white", size  =2.5)+
  # geom_vline(data=lines,aes(xintercept = Dates), show.legend = F)+
  # scale_linetype_manual(values = c("solid","84"),
  #                       limits = c("Thermocline","Outtake pipe"),  
  #                       name= NULL)+

```{r Make turbidity plot}

wer <- data.frame(
  data= c(rep("CTD_turb",12)),
  var = c(rep("Turbidity_NTU",12)),
  Res = c(rep("FCR",6), rep("BVR",6)),
  Years = c(rep(2018:2023,2))
)

make_turb_heat_map(
  data= temp_df,
  sample_dates1 = CTD_turb_casts,
  turnovers = turnover, 
  y_lim = c(0, 100),
  custom_heatmap_palette = blue2green2red(60),
  y_units = "Turbidity (NTU)",
  output_file = "figures/SedTraps_turbidity_2018_2023.jpeg"
)
